---
title: "p8105_hw1_amv2187"
author: "Alyssa Vanderbeek"
date: "21 September 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```


## Problem 1

```{r p1}
n = 10 # 10 rows in the following tbl_df

# Create tbl_df 
p1_df = tibble(
  unif_10 = runif(n = n, min = 0, max = 5), # random vector of size 10 selected from uniform [0,5]
  greater_than_2 = ifelse(unif_10 > 2, T, F), # logical vector. TRUE if value generated in unif_10 greater than 2; FALSE if less than or equal to 2
  char_vec = rep('a', n), # character vector of length 10,
  factor_vec = c(rep('Y', n/2), rep('N', n/2)) # factor vector of length 10
)

# Take mean of each column
mean(p1_df$unif_10)
mean(p1_df$greater_than_2)
mean(p1_df$char_vec)
mean(p1_df$factor_vec)
```

Taking the mean of the numeric and logical vectors in 'p1_df' is successful; taking the mean of the character and factor vectors is not. This is intuitive for the numeric vector. In the case of the logical vector, the function base::mean automatically converts logical TRUE/FALSE to numeric 1/0, and takes the arithmetic average. Conversely, characters and factors cannot be converted to a numeric format in any default way, and thus taking the mean cannot be done. 
